Automated Formal Synthesis of Digital Controllers for State-Space Physical Plants

### 2017-01-25 cav2017/cav2017.tex
Some stuff in the results

@@

\begin{tabular}{| r | c | l | r | r |}
\hline
\# & Benchmark  & $\mathcal{F}_{\langle I_c,F_c \rangle}$ & time for approach 1  & time for approach 2 \\\hline
1 & Ball Maglev & & & \\
2 & Cruise Control & & & \\
3 & DC Motor& & & \\
4 & Helicopter & & & \\
5 & Inverted Pendulum 1& & & \\
6 & Inverted Pendulum 2& & & \\
7 & Magnetic Pointer& & & \\
8 & Magnetic Suspension& & & \\
9 & Pendulum& & & \\
10 & Suspension& & & \\
11 & Tape Driver & & & \\
12 & Uscgtamper & & & \\
13 & Satellite & & & \\\hline

\end{tabular}
\caption{Experimental results}
\end{table}

>>>>

We give the run-times required to synthesize a stable controller for each
benchmark in Table~\ref{tab:results}.  
Here \textit{Benchmark} is the name of the employed
benchmark, $\mathcal{F}_{\langle I_p,F_p \rangle}$ is the fixed-point precision used to model the plant, while \textit{Time}
is the total time (in seconds) required to synthesize a stable controller
for the given plant, for approach 1 and approach 2. The precision for the controller, $\mathcal{F}_{\langle I_c,F_c \rangle}$, is always chosen to be $I_c = 8, F_c = 8$.

For the majority of our benchmarks, the conjecture stands that the Acceleration back-end is faster than the basic multi-staged verification approach. However, it does fail to find solutions to XXX benchmarks, where the numbers given in the discretization matrices are really small.

The basic multi-staged verification approach finds X / X benchmarks, albeit in an expected slower time. The solutions that are not found are due to time-out or XXXX

@@

\begin{tabular}{| r | c | l | r | r |}
\hline
\# & Benchmark  & $\mathcal{F}_{\langle I_p,F_p \rangle}$ & time for approach 1  & time for approach 2 \\\hline
1 & Ball Maglev & & & \\
2 & Cruise Control & & & \\
3 & DC Motor& & & \\
4 & Helicopter & & & \\
5 & Inverted Pendulum 1& & & \\
6 & Inverted Pendulum 2& & & \\
7 & Magnetic Pointer& & & \\
8 & Magnetic Suspension& & & \\
9 & Pendulum& & & \\
10 & Suspension& & & \\
11 & Tape Driver & & & \\
12 & Uscgtamper & & & \\
13 & Satellite & & & \\\hline

\end{tabular}
\caption{Experimental results \label{tab:results}}
\end{table}

he median runtime for our benchmark set is XXXX.  Overall,
the average synthesis time amounts to approximately XXX minutes.  We
consider these times short enough to be of practical use to control
engineers, and thus affirm RQ1.

The
synthesized controllers were confirmed to be stable outside of our model
representation using MATLAB, positively answering RQ2.  A~link to the full
experimental environment, including scripts to reproduce the results, all
benchmarks and the tool, is provided in the
footnote.\footnote{\url{url.here.}}
